A Review of Lossless Data Compression Methods

### 2018-11-19 paper.tex
Updates...
Finish discussion of LZW.

\title{A Review of Lossless Data Compression Methods}
\author{Citoyen}

@@

The basic method introduced in Lempel and Ziv's original paper is
vulnerable to some significant drawbacks. For instance, since each
individual byte in the input can take up at most three bytes in the
output, it is possible that some pathological input data can have a
compressed form which is substantially larger, especially if the
sliding window is small. (Clearly, a highly entropic input is much
more likely to have fewer recurring prefixes within any given sliding
window, which is consistent with our result from
\Cref{imperfect-compression}) As such, this suggests a good jumping-off
point for creating improvements upon the original algorithm.

@@

The Lempel-Ziv-Welch compression algorithm was an extension of the
Lempel-Ziv algorithm which was introduced soon after the publication
of the original LZ77. \cite{LempelZivWelch} The LZW variant is
extremely widespread in applications; for instance, one of its many
uses is as part of the GIF image format.

@@

Another algorithm based on the Lempel-Ziv foundation is the DEFLATE
algorithm, codified in RFC 1951. \cite{RFC1951}

@@

>>>>

\title{A Review of Lossless Data Compression Methods}
\author{someone idk}

@@

The basic method introduced in Lempel and Ziv's original paper is
vulnerable to some significant drawbacks. For instance, since each
individual byte in the input can take up at most three bytes in the
output, it is possible that some pathological input data can have a
compressed form which is substantially larger, especially if the
sliding window is small. (Clearly, a highly entropic input is much
more likely to have fewer recurring prefixes within any given sliding
window. Thus a prefix code based on such an output would have a higher
average word length, which is consistent with our result from
\Cref{snct}.) Another drawback of the LZ method is its performance;
searching the sliding window for matches, as well as updating the
window prefix list, can be an expensive operation. As such, these
drawbacks suggest a good jumping-off point for creating improvements
upon the original algorithm.

@@

One such improvement was the Lempel-Ziv-Welch compression algorithm,
commonly referred to as LZW. It was created as an extension of the
Lempel-Ziv algorithm which was introduced soon after the publication
of the original LZ77. The LZW variant is extremely widespread in
applications; for instance, one of its many uses is as part of the GIF
image format. LZW's improvements upon the LZ algorithm are fairly
straightforward, but they allow for significant improvements to the
simplicity of implementation. According to the author, the LZW
algorithm can take operate at a speed of three clock cycles (CPU
instructions) per input symbol. \cite{LempelZivWelch}

LZW is able to achieve this speed by using a single symbol table for
the entire input, adaptively building up as the algorithm processes
it. Instead of using a sliding window, LZW instead begins by
initializing a string table with every single-character prefix. As it
parses the input, it uses a greedy algorithm to match strings from the
input to the strings already seen in the table. It does this by
checking if some prefix in the input has already been seen in the
table; if so, it appends the immediately next character from the input
to the prefix and queries the string table again. If, on the other
hand, the appended prefix is \emph{not} found, the algorithm outputs
the code of the prefix \emph{without} the next character appended (the
code for which is retrieved from the string table) and then adding the
appended prefix to the string table. The prefix is set to the last
character of the prefix and the process repeats.

As we can see, the entire algorithm can be succinctly summarized in a
few sentences and can also be (hopefully) easily understood. This
characteristic makes it useful for implementers, and also has benefits
in terms of performance. Since it uses a very simple process for
encoding, it is able to greatly reduce the number of clock cycles
needed for encoding or decoding each character. In addition, it is
also simple to implement performance-enhancing features, such as using
a tree data structure with hashing to store string prefixes, buffering
the input data to conserve memory, and so forth. Drawbacks of the LZW
method include lower compression ratios than other, more advanced
methods. For instance, the author claims a ratio of 1.8 on English
text, compared to a 2.4 ratio achieved by more sophisticated
algorithms. \cite{LempelZivWelch}

The LZ family of compression codes is massive, and LZW is just one
single member. Another, possibly even more widespread variant is the
DEFLATE algorithm.

@@

Another algorithm based on the Lempel-Ziv foundation is the DEFLATE
format, codified in RFC 1951. \cite{RFC1951} DEFLATE is not
``standardized'' by any recognized governing body, though it is very
widely used and has become a de facto standard by virtue of its use in
the \texttt{gzip} compression utility, as well as in the ubiquitous
\texttt{zlib} library. RFC 1951 specifies the technical minutia of the
implementation of the file format, as well as its algorithm itself. As
such, it is not useful to describe the full file format within this
paper, only the algorithm will be outlined.

@@

\section{Conclusion}
